Maenpuen \emph{et al.} --American Journal of Botany-- Appendix S1

### 2022-06-25 ms/SI.Rmd
update SI PDF

---
title: "Maenpuen *et al.* --American Journal of Botany-- Appendix S1"
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
#  - \usepackage{lineno}
#  - \linenumbers
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: FALSE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_args:
      - "--filter"
      - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

```{r caching, include=FALSE, eval=TRUE}
library(knitr)
library(tidyverse)
library(methods)
library(targets)
basename <- "LMA_method"
opts_chunk$set(fig.path = paste("figs/", sep = ""))
opts_chunk$set(tidy = FALSE,
               warning = FALSE,
               message = FALSE,
               comment = NA,
               verbose = TRUE,
               cache = FALSE,
               echo = FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')

# https://github.com/haozhu233/kableExtra/issues/47
options(kableExtra.auto_format = FALSE)
library(kableExtra)

# for dependency
targets::tar_load(yml)
#  for non-targets
# val <- yaml::yaml.load_file("../values.yml")
#val <- yaml::yaml.load_file("values.yml")
```

@@

```{r, echo=FALSE}
library(jsonlite)
#site <- fromJSON("../data/site_info.json")
site <- fromJSON("data/site_info.json")
site |>
  kable(format = "html") |>
  # kable_styling() |>
  kable_styling(latex_options = "scale_down")
  #kableExtra::landscape()
```

@@

```{r, eval=TRUE, echo=FALSE}
targets::tar_load(dm_glmm_tab)
dm_glmm_tab |>
  kable(format = "html") |>
  kable_styling()
```

@@

```{r, include=FALSE}
targets::tar_load(lma_ld_plot)
```

![](../figs/lma_ld.png){ width="600" style="display: block; margin: 0 auto" }

@@

```{r, include=FALSE}
targets::tar_load(coef_sp_punch1_add_plot)
```

![](../figs/coef_sp_punch1_add.png)

@@

```{r, include=FALSE}
targets::tar_load(sma_sep_plot)
```

![](../figs/sma_sep.png){ width="400" style="display: block; margin: 0 auto" }

@@

```{r, include=FALSE}
targets::tar_load(ratio_dm_plot)
```

![](../figs/ratio_dm.png){ width="400" style="display: block; margin: 0 auto" }

>>>>

---
title: "Maenpuen *et al.* --American Journal of Botany-- Appendix S1"
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
#  - \usepackage{lineno}
#  - \linenumbers
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: FALSE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: yes
    toc: yes
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    # pandoc_args:
    #   - "--filter"
    #   - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

```{r caching, include=FALSE, eval=TRUE}
library(knitr)
library(tidyverse)
library(methods)
library(targets)
library(here)
library(kableExtra)
basename <- "LMA_method"
opts_chunk$set(fig.path = paste("figs/", sep = ""))
opts_chunk$set(tidy = FALSE,
               warning = FALSE,
               message = FALSE,
               comment = NA,
               verbose = TRUE,
               cache = FALSE,
               echo = FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')

# https://github.com/haozhu233/kableExtra/issues/47
options(kableExtra.auto_format = FALSE)
# for dependency
#targets::tar_load(yml)
#  for non-targets
# val <- yaml::yaml.load_file("../values.yml")
#val <- yaml::yaml.load_file("values.yml")
```

@@

```{r, echo=FALSE, caption = "hopge"}
library(jsonlite)
#site <- fromJSON("../data/site_info.json")
#site <- fromJSON("data/site_info.json")
site <- fromJSON(here("data", "site_info.json"))
site |>
  kable(format = "latex",
    caption = "Site information.
              MAT: mean annual temperature,
              MAP: mean annual precipitation,
              CV: coefficient of variation") |>
  # kable_styling() |>
  kable_styling(latex_options = "scale_down") |>
  # column_spec(13:16, width = "2cm") |>
  column_spec(1:16, width = "2cm") |>
  kableExtra::landscape()
```

@@

```{r, eval=TRUE, echo=FALSE}
dm_glmm <- read_csv(here("data", "dm_glmm.csv"))
dm_glmm |>
  kable(format = "latex") |>
  kable_styling()
```

@@

![](../figs/lma_ld.pdf){ width="600" style="display: block; margin: 0 auto" }

@@

![](../figs/coef_sp_punch1_add.pdf)

@@

![](../figs/sma_sep.pdf){ width="400" style="display: block; margin: 0 auto" }

@@

![](../figs/ratio_dm.pdf){ width="400" style="display: block; margin: 0 auto" }

### 2022-06-25 ms/SI.tex
update SI PDF

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*,table}{xcolor}
%
\documentclass[
  12pt,
  a4paper,
,tablecaptionabove
]{scrartcl}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\definecolor{default-linkcolor}{HTML}{A50000}
\definecolor{default-filecolor}{HTML}{A50000}
\definecolor{default-citecolor}{HTML}{4077C0}
\definecolor{default-urlcolor}{HTML}{4077C0}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Maenpuen et al.~Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)},
  hidelinks,
  breaklinks=true,
  pdfcreator={LaTeX via pandoc with the Eisvogel template}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
% add backlinks to footnote references, cf. https://tex.stackexchange.com/questions/302266/make-footnote-clickable-both-ways
\usepackage{footnotebackref}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{lineno}
\linenumbers

@@

\title{Maenpuen et al.~Appendix S1-7: Sources and consequences of
mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
\date{}

@@

%
% variables for title and author
%
\usepackage{titling}
\title{Maenpuen et al.~Appendix S1-7: Sources and consequences of
mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
\author{}

@@

\definecolor{table-row-color}{HTML}{F5F5F5}
\definecolor{table-rule-color}{HTML}{999999}

%\arrayrulecolor{black!40}
\arrayrulecolor{table-rule-color}     % color of \toprule, \midrule, \bottomrule
\setlength\heavyrulewidth{0.3ex}      % thickness of \toprule, \bottomrule
\renewcommand{\arraystretch}{1.3}     % spacing (padding)

@@

\fancypagestyle{eisvogel-header-footer}{
  \fancyhead{}
  \fancyfoot{}
  \lhead[]{Maenpuen et al.~Appendix S1-7: Sources and consequences of
mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
  \chead[]{}
  \rhead[Maenpuen et al.~Appendix S1-7: Sources and consequences of
mismatch between leaf disc and whole-leaf leaf mass per area (LMA)]{}
  %\lfoot[\thepage]{}
  \cfoot[]{}
  \cfoot[]{\thepage}
  \renewcommand{\headrulewidth}{0.0pt}
 % \renewcommand{\footrulewidth}{0.0pt}
 % \renewcommand{\headrulewidth}{0.4pt}
 % \renewcommand{\footrulewidth}{0.4pt}
}
\pagestyle{eisvogel-header-footer}

@@

\hypertarget{appendix-s1}{%
\section{Appendix S1:}\label{appendix-s1}}

Site information. MAT: mean annual temperature, MAP: mean annual
precipitation, SPEI: Standardized Precipitation Evapotranspiration
Index.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0741}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.2469}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0926}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0556}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0617}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1173}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1049}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Site name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Vegetation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Elevation (m)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Locations
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
MAT (℃)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
MAP (mm)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dry period (month)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Canopy height (m)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Species number
\end{minipage} \\
\midrule
\endhead
Bubeng & Tropical forest (TRF) & 780 & 21°37'N, 101°35' E & 21 & 1532 &
6 & 35-45 & 60 \\
Ailao-shan & Subtropical evergreen wet forest (STF) & 2500 &
24°32'N,101°01'E & 11.7 & 1931 & - & 25 & 47 \\
Yuanjiang & Hot-dry savanna (HDS) & 480 & 23°28'N, 102°10'E & 24.7 &
732.8 & 6 & 4-6 & 34 \\
Yakushima & Warm-temperate forest & 14 - 1748 & 30°38'N, 130°62'E & 19.4
& 4477 & - & - & 193 \\
\bottomrule
\end{longtable}

The site information and climate data referred to Fei et al.
(\protect\hyperlink{ref-Fei2018}{2018}) and Song et al.
(\protect\hyperlink{ref-Song2017}{2017}). The 6-month-SPEI data were
extracted from the Global SPEI database
(\url{http://spei.csic.es/map/maps.html\#months=1\#month=7\#year=2019}).

@@

\hypertarget{appendix-s2}{%
\section{Appendix S2:}\label{appendix-s2}}

@@

\includegraphics[width=6.25in,height=\textheight]{../figs/fig1.png}

@@

\hypertarget{appendix-s3}{%
\section{Appendix S3:}\label{appendix-s3}}

Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry
mass for the leaf disc, (b) leaf thickness, and (c) leaf area. (b) and
(c) follow the same legend. All the relationships were heteroscedastic
(unequal variance, \emph{p} \textless{} 0.001; all the samples were
analyzed together in (a)). Samples with small total dry mass, thin
leaves, and larger leaves tended to show greater variance.

\includegraphics{../figs/LMAratio2.png}

@@

\hypertarget{appendix-s4}{%
\section{Appendix S4:}\label{appendix-s4}}

Summary of multiple regression for log-transformed total dry mass of
leaf discs. The leaf punch size is described as an effect of `1.0 cm
diameter' compared with `0.6 cm diameter'.

\begin{longtable}[]{@{}lllll@{}}
\toprule
& Estimate & SE & t-value & \emph{P} value \\
\midrule
\endhead
(Intercept) & -4.86 & 0.012 & -410 & \textless{} 0.001 \\
log(Leaf thickness) & 0.223 & 0.009 & 23.7 & \textless{} 0.001 \\
log(Leaf area) & -0.092 & 0.01 & -9.27 & \textless{} 0.001 \\
Large leaf punch & 0.391 & 0.021 & 18.7 & \textless{} 0.001 \\
\bottomrule
\end{longtable}

@@

\hypertarget{appendix-s5}{%
\section{Appendix S5:}\label{appendix-s5}}

Relationships between species mean leaf mass per area (LMA) determined
by using whole leaves and leaf discs. Species groups are divided into
four categories on the basis of the medians of the leaf size and leaf
thickness across all the species. Estimates obtained by different leaf
punches are plotted separately in different colors. All the correlations
are significant (\emph{P} \textless{} 0.001).

\includegraphics[width=6.25in,height=\textheight]{../figs/LMA_sp_gr_both.png}

\hypertarget{appendix-s6}{%
\section{Appendix S6:}\label{appendix-s6}}

Relationships between petiole to leaf dry mass ratio and (a) leaf area
and (b) whole-leaf to leaf disc LMA ratio. Blue solid lines indicate
ordinary least squares (OLS) regressions. The 95\% confidence intervals
are presented as the shaded area. All the correlations are significant
(\emph{P} \textless{} 0.001).

\includegraphics[width=6.25in,height=\textheight]{../figs/petiole.png}

\hypertarget{appendix-s7}{%
\section{Appendix S7:}\label{appendix-s7}}

Relationships between coefficient of variation (CV) in LMA determined by
using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and
(b) 1.0 cm diameter leaf punch. Dashed lines indicate 1:1 lines. Blue
solid lines indicate standardized major axis regressions. The 95\%
confidence intervals are presented as the shaded area. All the
correlations are significant (\emph{P} \textless{} 0.01). Note that the
axes are square root scales.

\includegraphics[width=6.25in,height=\textheight]{../figs/fig_cv2.png}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Fei2018}{}}%
Fei, X., Q. Song, Y. Zhang, Y. Liu, L. Sha, G. Yu, L. Zhang, et al.
2018. \href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon
exchanges and their responses to temperature and precipitation in forest
ecosystems in {Yunnan}, {Southwest China}}. \emph{Science of The Total
Environment} 616--617: 824--840.

\leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
Song, Q.-H., Y.-P. Zhang, L.-Q. Sha, X.-B. Deng, Y. Deng, C.-S. Wu,
Z.-Y. Lu, et al. 2017.
\href{https://doi.org/10.3832/ifor2223-010}{Canopy temperature
variability in a tropical rainforest, subtropical evergreen forest, and
savanna forest in {Southwest China}}. \emph{iForest - Biogeosciences and
Forestry} 10: 611.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*,table}{xcolor}
%
\documentclass[
  12pt,
  a4paper,
,tablecaptionabove
]{scrartcl}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\definecolor{default-linkcolor}{HTML}{A50000}
\definecolor{default-filecolor}{HTML}{A50000}
\definecolor{default-citecolor}{HTML}{4077C0}
\definecolor{default-urlcolor}{HTML}{4077C0}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Maenpuen et al. --American Journal of Botany-- Appendix S1},
  hidelinks,
  breaklinks=true,
  pdfcreator={LaTeX via pandoc with the Eisvogel template}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
% add backlinks to footnote references, cf. https://tex.stackexchange.com/questions/302266/make-footnote-clickable-both-ways
\usepackage{footnotebackref}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\title{Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
S1}
\date{}

@@

%
% variables for title and author
%
\usepackage{titling}
\title{Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
S1}
\author{}

@@

@@

\fancypagestyle{eisvogel-header-footer}{
  \fancyhead{}
  \fancyfoot{}
  \lhead[]{Maenpuen \emph{et al.} --American Journal of Botany--
Appendix S1}
  \chead[]{}
  \rhead[Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
S1]{}
  %\lfoot[\thepage]{}
  \cfoot[]{}
  \cfoot[]{\thepage}
  \renewcommand{\headrulewidth}{0.0pt}
 % \renewcommand{\footrulewidth}{0.0pt}
 % \renewcommand{\headrulewidth}{0.4pt}
 % \renewcommand{\footrulewidth}{0.4pt}
}
\pagestyle{eisvogel-header-footer}

@@

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{appendix-s1}{%
\section{Appendix S1:}\label{appendix-s1}}

Supporting Tables and Figures.

@@

\hypertarget{table-s1}{%
\section{Table S1:}\label{table-s1}}

Site information. MAT: mean annual temperature, MAP: mean annual
precipitation, CV: coefficient of variation

\begin{landscape}\begin{table}

\caption{\label{tab:unnamed-chunk-1}Site information.
              MAT: mean annual temperature,
              MAP: mean annual precipitation,
              CV: coefficient of variation}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}}
\hline
Data name & Site name & Vegetation & Elevation (m) & Location & MAT (℃) & MAP (mm) & Dry period (month) & Canopy height (m) & Leaf thickness & Leaf disc thickness & Leaf punch diameter (cm) & Number of species for species means & Number of individuals for individuals means & Number of species for CV & Number of individuals for CV\\
\hline
Yunnan & Bubeng & Tropical forest (TRF) & 780 & 21°37'N, 101°35'E & 21 & 1532.0 & 6 & 35-45 & Measured & Measured & 0.6 & 60 & 366 & 60 & 366\\
\hline
Yunnan & Ailao-shan & Subtropical evergreen wet forest (STF) & 2500 & 24°32'N, 101°01'E & 11.7 & 1931.0 & - & 25 & Measured & Measured & 0.6 & 47 & 282 & 47 & 282\\
\hline
Yunnan & Yuanjiang & Hot-dry savanna  (HDS) & 480 & 23°28'N, 102°10'E & 24.7 & 732.8 & 6 & 6-Apr & Measured & Measured & 0.6 & 34 & 204 & 33 & 203\\
\hline
Yakushima & Yakushima & Warm-temperate forest & 14 - 1748 & 30°38'N, 130°62'E & 8.1 - 19.4 & 4477.0 & - & - & Measured & Not-measured & 1.0 & 193 & 607 & 5 & 26\\
\hline
\end{tabular}}
\end{table}
\end{landscape}

The site information and climate data in Yunnan, referred to Fei et al.
(\protect\hyperlink{ref-Fei2018}{2018}), and Song et al.
(\protect\hyperlink{ref-Song2017}{2017}). MAT and MAP of Yakushima were
obtained from the Yakushima meteorological station and Eguchi
(\protect\hyperlink{ref-Eguchi2006}{2006}).

\hypertarget{table-s2}{%
\section{Table S2:}\label{table-s2}}

Summary of a linear mixed model for log-transformed total dry mass of
leaf discs for each tree individual. Species was used as a random
intercept. The leaf punch size is described as an effect of `0.6 cm
diameter' compared with `1.0 cm diameter'.

\begin{table}
\centering
\begin{tabular}{r|r|r|r|l}
\hline
Estimate & SE & DF & t-value & *P* value\\
\hline
-4.410 & 0.013 & 1030 & -333.00 & < 0.001\\
\hline
0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
\hline
-0.061 & 0.009 & 1030 & -6.94 & < 0.001\\
\hline
0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
\hline
-0.500 & 0.020 & 332 & -25.60 & < 0.001\\
\hline
\end{tabular}
\end{table}

\hypertarget{figure-s1}{%
\section{Figure S1:}\label{figure-s1}}

Detailed sampling protocol for whole-leaf and leaf disc LMA.

\includegraphics{../figs/S2.jpeg}

\hypertarget{figure-s2}{%
\section{Figure S2:}\label{figure-s2}}

@@

\includegraphics[width=6.25in,height=\textheight]{../figs/lma_ld.pdf}

@@

\hypertarget{figure-s3}{%
\section{Figure S3:}\label{figure-s3}}

Standardized regression coefficients modelig the effects of leaf tissue
density, leaf area, leaf thickness, punch size, and their interactios
(a) on the mean estimates of whole-leaf LMA, and (b) on the estimated
variance of whole-leaf LMA. The leaf disc LMA was used for the baseline
mean of the whole-leaf LMA. Thick and thin lines indicate 90\% and 95\%
credible intervals, respectively. Circles show posterior means of
coefficients. Circles filled with blue indicate significant effects and
white indicate non-significance effects.

\includegraphics{../figs/coef_sp_punch1_add.pdf}

@@

\hypertarget{figure-s4}{%
\section{Figure S4:}\label{figure-s4}}

Relationships between species mean leaf mass per area (LMA) determined
by using whole-leaves and leaf discs for species obtained with leaf
punches of different diameters. Dashed lines indicate 1:1 lines. Blue
solid lines indicate standardized major axis (SMA) regressions. The 95\%
confidence intervals are resented as the shaded area. The correlation is
significant (\emph{P} \textless{} 0.001).

\includegraphics[width=4.16667in,height=\textheight]{../figs/sma_sep.pdf}

@@

\hypertarget{figure-s5}{%
\section{Figure S5:}\label{figure-s5}}

Relationships between whole-leaf LMA : disc leaf LMA and total dry mass
for the leaf disc. The relationships was heteroscedastic (unequal
variance, \emph{p} \textless{} 0.001; all the samples were analyzed
together). Samples with small total dry mass tended to show greater
variance.

\includegraphics[width=4.16667in,height=\textheight]{../figs/ratio_dm.pdf}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Eguchi2006}{}}%
Eguchi, T. 2006. Climate. Yakushima, 3--26. {Asakura Shoten}, {Tokyo (in
Japanese)}.

\leavevmode\vadjust pre{\hypertarget{ref-Fei2018}{}}%
Fei, X., Q. Song, Y. Zhang, Y. Liu, L. Sha, G. Yu, L. Zhang, et al.
2018. \href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon
exchanges and their responses to temperature and precipitation in forest
ecosystems in {Yunnan}, {Southwest China}}. \emph{Science of The Total
Environment} 616--617: 824--840.

\leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
Song, Q. H., Y. P. Zhang, L. Q. Sha, X. B. Deng, Y. Deng, C. S. Wu, Z.
Y. Lu, et al. 2017. \href{https://doi.org/10.3832/ifor2223-010}{Canopy
temperature variability in a tropical rainforest, subtropical evergreen
forest, and savanna forest in {Southwest China}}. \emph{iForest -
Biogeosciences and Forestry} 10: 611.
